Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/contributions.tex
Editing pass, two more passes before submission

\subsection*{Part II: Most Significant Contributions to Research \& Development}
%\textit{Describe your role in research, clarify your contribution, provide
%    details on significance of tech report, indicate collaborations, discuss
%relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
I contributed to this report by producing all the theoretical and simulation
results, though I received an abundance of advice from my supervisor, Fady
Alajaji. 
I also wrote the report in its entirety.
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019, and it motivated further research [1].

@@

    \item \textbf{Radar Developer, University of Toronto, 2018}.
        In the group project for a graduate course, I worked with three other
        students to write software which reads data from a radar device.
        This project taught me several engineering skills.
        First, I improved my project management skills by keeping our group
        meetings organized, and by separating the tasks in such a way
        that everyone was learning something from the project.
        I learned to read hardware documentation and to wire a device from
        schematics.
        I wrote networking code in Python to interface with the
        device, and validated the hardware's capabilities for myself by
        creating appropriate test environments. 
        All these skills will be beneficial for my PhD research when I build a
        robotic monkey.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}.
        For my undergraduate thesis, I worked with my peers to design an image
        filtering algorithm by applying theoretical results from information theory.
        During this project I learned to perform a basic literature review,
        and to manage deadlines with a supervisor.
        I also learned to write reports in LaTeX,
        and my thesis group worked together on code optimization: we learned to
        convert equations into matrix form to take advantage of hardware
        optimization; we parallelized our code so our algorithm would run faster
        through multithreading; we ported MATLAB code to C++ to achieve even
        faster results; and we created a GUI so we could test our code quickly
        and easily.

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career because it convinced
        me to pursue research in robotics.
        Working at Neptec exposed me to many areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        After completing this project, I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        At Neptec I also learned to work on large software projects, where multiple people work
        together on the same code; 
        and I became extremely proficient at software development, a skill which
        has served me well in my research experiments on physical robots.

@@

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course I teach improves my communication skills, and each tutorial gives
    me the opportunity to make the course material more fun and engaging.
    I focus most on attaining high levels of student participation by being
    kind and non-judgemental, which makes students feel
    comfortable enough to ask whatever question crosses their mind.

@@

I take pride in my teaching, communication, and leadership abilities, yet I
remain aware that these can always be improved.
Obtaining an NSERC scholarship will provide me with the financial liberty to
participate in more volunteer roles, where I can better myself while giving back to my
community.

>>>>

\subsection*{Part II: Most Significant Contributions to Research \& Development}
%\textit{Describe your role in research, clarify your contribution, provide
%    details on significance of tech report, indicate collaborations, discuss
%relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
I wrote this report in its entirety, and I contributed all the theoretical and
simulation results (with abundant advice from my supervisor, Fady Alajaji).
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019, and it motivated further research in [1].

@@

    \item \textbf{Radar Developer, University of Toronto, 2018}.
        In the group project for a graduate course, I worked with three other
        students to write software which reads data from a radar device.
        This project improved my project management skills, as I kept our group
        meetings organized and separated the project tasks in such a way
        that everyone was challenged appropriately.
        I learned to read hardware documentation and to wire a device from
        schematics.
        I wrote networking code in Python to interface with the
        device, and validated the hardware's capabilities for myself by
        creating appropriate test environments. 
        All these skills will be beneficial for my PhD research, where I will
        collaborate with labmates to build a robotic monkey.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}.
        For my undergraduate thesis, I worked with my peers to design an image
        filtering algorithm by applying theoretical results from information theory.
        During this project I learned to perform a basic literature review,
        and to manage deadlines with a supervisor.
        I also learned to write reports in LaTeX,
        and my group worked together on code optimization: we learned to
        convert equations into matrix form to take advantage of hardware
        optimization; we parallelized our code so our algorithm would run faster
        through multithreading; we ported MATLAB code to C++ to achieve even
        faster results; and we created a GUI so we could test our code quickly
        and easily.

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career because it convinced
        me to pursue research in robotics.
        Working at Neptec exposed me to many areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        After completing this project, I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        At Neptec I also learned to work on large software projects,
        and I became extremely proficient at software development, a skill which
        has served me well in all aspects of my research.

@@

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course I teach improves my communication skills, and each tutorial gives
    me the opportunity to make the course material more fun and engaging.
    I focus most on attaining high levels of student participation by being
    kind and non-judgemental, which makes students feel
    comfortable enough to ask more questions.

@@

I take pride in my teaching, communication, and leadership abilities, yet I
remain aware that these can always be improved.
Obtaining an NSERC scholarship will provide me with the financial liberty to
participate in more volunteer roles, where I can improve my skills while giving back to my
community.

### 2021-09-20 latex/nserc/proposal.tex
Editing pass, two more passes before submission

%---------- Main Content ----------%
A robotic monkey swings through trees in a Mexican jungle, capturing valuable
wildlife data without disturbing the local environment. 
In the nearby city, a robotic police dog runs through the streets, weaving through
pedestrians' legs to catch a thief.
It passes a traveling circus group, where robot gymnasts perform elaborate
routines in front of an awestruck audience.
This world sounds like science fiction, but it is truly within sight;
our research will enable roboticists to accurately recreate human and animal
behaviour in their robots.
The future we imagined will become a present-day reality.

>>>>

%---------- Main Content ----------%
A robotic monkey swings through jungle trees, capturing valuable
wildlife data without disturbing the local environment. 
In a nearby city, a robotic police dog runs through the streets, weaving through
pedestrians' legs to catch a thief.
It passes a traveling circus group, where robot gymnasts perform elaborate
routines in front of an awestruck audience.
This world sounds like science fiction, but it is truly within sight;
the research we propose below will enable roboticists to accurately recreate
human and animal behaviour in their robots.
This world we imagined can become a present-day reality.
